Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-28 draft/ms_v5.tex
Almost ready

@@

@@

% ALEXIE: not necessary
    %The majority of the galaxies in our synthetic galaxy samples are  are faint
    %($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec).
    %It is very challenging to obtain accurate photometry good photometric quality of these galaxies, which 
    %is crucial to key scientific goals of the HSC survey.
    %The selected samples do not provide enough bright or large galaxies to test.
    %Therefore, we will supplement results for these galaxies using better samples
    %in the future.

@@

@@

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Astrometric Calibration
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_astrometry}
    \end{center}
    \caption{
        Astrometric accuracy for synthetic stars (\textbf{left}) and galaxies
        (\textbf{right}). 
        We show the differences between the input R.A and Dec and the coordinates 
        measured on the \coadd{} images. 
        Hexagonal bins (filled histogram) and contours (solid-line histogram) are 
        for synthetic objects from \tracts{} with good and bad seeing conditions, 
        respectively.
        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.     
        \song{We find that xxxxxx}.
        }
    \label{fig:astrometry}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We inject synthetic objects into single-\visit{} images using the initial (and 
    less accurate) astrometric calibration.
    During the image stacking step, the joint calibration process improves the
    astrometric solutions.
    Therefore, differences between the input and output coordinates from \synpipe{}
    can help us understand how much has the joint calibration step changes the 
    astrometric calibration.

    Fig \ref{fig:astrometry} shows the distribution of astrometric offsets for 
    synthetic stars and galaxies in \texttt{goodSeeing} and \texttt{badSeeing} 
    \tracts{}.
    We find small systematic offsets at the ${\sim}10$--20 mas level.
    The two \tracts{} show different systematic offsets.
    In the same \tracts{}, synthetic stars and galaxies show similar offsets, but 
    the scatter for galaxies is slightly larger than stars due to their extended 
    nature.

>>>>

	The precisions and accuracies of \forced{} PSF magnitudes shown here are 
	summarized in Table \ref{tab:mag}

@@

	The statistical uncertainties of \forced{} PSF colors are summarized in 
	Table \ref{tab:color}

@@

@@

	The precisions and accuracies of \forced{} \cmodel{} magnitudes shown here are 
	summarized in Table \ref{tab:mag}

@@

	The statistical uncertainties of \forced{} \cmodel{} colors are summarized in 
	Table \ref{tab:color}

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Astrometric Calibration
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_astrometry}
    \end{center}
    \caption{
        Astrometric accuracy for synthetic stars (\textbf{left}) and galaxies
        (\textbf{right}). 
        We show the differences between the input R.A and Dec and the coordinates 
        measured on the \coadd{} images. 
        Hexagonal bins (filled histogram) and contours (solid-line histogram) are 
        for synthetic objects from \tracts{} with good and bad seeing conditions, 
        respectively.
        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.     
        It shows that the initial astrometric calibration is already very accurate,  
        and it also suggests that \hscpipe{} can find the centroids of stars and 
        galaxies with precisions that are consistent with the astrometric calibration
        uncertainty under moderately different seeing conditions.
        }
    \label{fig:astrometry}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We inject synthetic objects into single-\visit{} images using the initial (and 
    less accurate) astrometric calibration.
    During the image stacking step, the joint calibration process improves the
    astrometric solutions.
    Therefore, differences between the input and output coordinates from \synpipe{}
    can help us understand how much has the joint calibration step changes the 
    astrometric calibration, and how well can \hscpipe{} measure the central 
    coordinates of stars and galaxies.

    Fig \ref{fig:astrometry} shows the distribution of astrometric offsets for 
    synthetic stars and galaxies in \texttt{goodSeeing} and \texttt{badSeeing} 
    \tracts{}.
    We find small systematic offsets at the ${\sim}10$--20 mas level, which is similar 
    to the uncertainties of astrometric calibration quoted in \citet{HSCDR1}.
    The two \tracts{} show different systematic offsets, while the synthetic stars and
    galaxies show coherent offsets in the same \tract{}.
    This shows that the initial astrometric calibration of HSC has very reasonable 
    accuracy.  
    It also suggests that \hscpipe{} can find the centroids of stars and galaxies 
    with precisions that are consistent with the astrometric calibration uncertainty
    under moderately different seeing conditions.
